---
title: "An introduction to `HDTSA`"
output: rmarkdown::html_vignette
# output: rmarkdown::github_document
vignette: >
  %\VignetteIndexEntry{An introduction to HDTSA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{HCmodelSets}
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = F,
  message = F
)
```

# HDTSA

<!-- badges: start -->

<!-- badges: end -->

The purpose of `HDTSA` is to address a range of high-dimensional time series problems, which includes solutions to a series of statistical issues, primarily comprising:Procedures for high-dimensional time series analysis including factor analysis proposed by Lam and Yao (2012) [<doi:10.1214/12-AOS970>](https://doi.org/10.1214/12-AOS970) and Chang, Guo and Yao (2015) [<doi:10.1016/j.jeconom.2015.03.024>](https://doi.org/10.1016/j.jeconom.2015.03.024), martingale difference test proposed by Chang, Jiang and Shao (2022) [<doi:10.1016/j.jeconom.2022.09.001>](https://doi.org/10.1016/j.jeconom.2022.09.001), principal component analysis proposed by Chang, Guo and Yao (2018) [<doi:10.1214/17-AOS1613>](https://doi.org/10.1214/17-AOS1613), identifying cointegration proposed by Zhang, Robinson and Yao (2019) [<doi:10.1080/01621459.2018.1458620>](https://doi.org/10.1080/01621459.2018.1458620), unit root test proposed by Chang, Cheng and Yao (2021) [<doi:10.1093/biomet/asab034>](https://doi.org/10.1093/biomet/asab034), white noise test proposed by Chang, Yao and Zhou (2017) [<doi:10.1093/biomet/asw066>](https://doi.org/10.1093/biomet/asw066), CP-decomposition for high-dimensional matrix time series proposed by Chang, He, Yang and Yao (2023) [<doi:10.1093/jrsssb/qkac011>](https://doi.org/10.1093/jrsssb/qkac011) and Chang, Du, Huang and Yao (2024+), and Statistical inference for high-dimensional spectral density matrix porposed by Chang, Jiang, McElroy and Shao (2023) [<doi:10.48550/arXiv.2212.13686>](https://doi.org/10.48550/arXiv.2212.13686).

## Installation

You can install the released version of `HDTSA` from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("HDTSA")
```

Or try the development version on GitHub:

``` r
# install.packages("devtools")
devtools::install_github("Linc2021/HDTSA")
```

## Example

This is a basic example which shows you how to solve a unit root test problem :

```{r example}
library(HDTSA)
N=100
Y=arima.sim(list(ar=c(0.9)), n = 2*N, sd=sqrt(1))
con_vec=c(0.45,0.55,0.65)
lagk.vec=c(0,1,2)
UR_test(Y,lagk.vec=lagk.vec, con_vec=con_vec,alpha=0.05)
UR_test(Y,alpha=0.05)
```

Here, we have provided just one example. You can use functions within the package `HDTSA` to solve other problems. For details, please refer to

``` r
help("HDTSA")
```

## Bug report

Please send an email to Chen Lin([linchen\@smail.swufe.edu.cn](mailto:linchen@smail.swufe.edu.cn){.email}).
